Title Goes Here

### 2024-03-12 analysis/paper/paper.qmd
migrate from Rmd to qmd

---
title: "Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam"
author:
  - Pham Thanh Son:
      email: thanhson9119@gmail.com
      institute: [IofA]
      correspondence: true
  - Quinn Habedank:
      email: fl@oneoeurhg.edu
      institute: [UofW]
      correspondence: true
  - Ben Marwick:
      email: bmarwick@uw.edu
      institute: [UofW]
      correspondence: false
institute:
  - IofA: Vien Khao co hoc
  - UofW: University of Washington 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      number_sections: false
      global_numbering: true
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# Abstract

Flaked stone artefacts from Southeast Asia typically lack visually distinctive and strongly patterned forms, which can make them challenging to analyze and interpret. As a result, many of the cultural dynamics of Pleistocene hunter-gatherers of this region are poorly understood. We use 2D shape data to hypothesize a relationship between unretouched flake shape and assemblage reduction intensity at Mau A, an early Holocene archaeological site in northern Vietnam. We apply a Principal Components Analysis to the flake landmarks to investigate shape variation throughout the reduction sequence (measured by dorsal cortex coverage). We find that flake shape varies by reduction stage, primarily through differences in flake length and width. Our results suggest that flake shape is sensitive to assemblage reduction intensity, and may give useful comparative insights when other attributes show little variation. These results are important for understanding stone artefact assemblages from Southeast Asia which often yield little variation when analysed with traditional approaches.

## Introduction
<!-- BM: In this section we need to review in very precise detail, previous work on investigating flake shape and identifying what affects flake shape, especially the Borel papers, not just in Southeast Asia, but anywhere in the world, Look in Borel to see what papers they cite, and we should summarise the most relevant of those, e.g. the previous papers that are most similar to our project  -->

@@

## Methods

```{r, schematic-figure, fig.cap="Schematic figure showing the location of our landmarks on a hypothetical flake"}
knitr::include_graphics(here::here("analysis/figures/flake-measurements-schematic-figure-temp.png"))
```

@@

## Results

@@

## References

@@

<div id="refs"></div>

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

>>>>

---
title: "Title Goes Here"
author:
  - Pham Thanh Son:
      correspondence: "no"
      email: thanhson9119@gmail.com
      orcid: 0000-0003-1689-0557
      institute:
        - IofA
  - Quinn Habedank:
      correspondence: "no"
      institute: UofW
  - Seungki Kwak:
      correspondence: "no"
      institute: fosg
      orcid: 0000-0003-1689-0559
  - Ben Marwick:
      correspondence: "yes"
      orcid: 0000-0001-7879-4531
      institute: UofW
institute:
  - UofW:
      name: University of Washington 
      address: Seattle, WA, USA
  - IofA: Vien Khao co hoc
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Flaked stone artefacts from Southeast Asia typically lack visually distinctive and strongly patterned forms, which can make them challenging to analyze and interpret. As a result, many of the cultural dynamics of Pleistocene hunter-gatherers of this region are poorly understood. We use 2D shape data to hypothesize a relationship between unretouched flake shape and assemblage reduction intensity at Mau A, an early Holocene archaeological site in northern Vietnam. We apply a Principal Components Analysis to the flake landmarks to investigate shape variation throughout the reduction sequence (measured by dorsal cortex coverage). We find that flake shape varies by reduction stage, primarily through differences in flake length and width. Our results suggest that flake shape is sensitive to assemblage reduction intensity, and may give useful comparative insights when other attributes show little variation. These results are important for understanding stone artefact assemblages from Southeast Asia which often yield little variation when analysed with traditional approaches.
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

<!-- BM: In this section we need to review in very precise detail, previous work on investigating flake shape and identifying what affects flake shape, especially the Borel papers, not just in Southeast Asia, but anywhere in the world, Look in Borel to see what papers they cite, and we should summarise the most relevant of those, e.g. the previous papers that are most similar to our project  -->

@@

# Methods

```{r}
#| label: schematic-figure
#| fig-cap: "Schematic figure showing the location of our landmarks on a hypothetical flake"

knitr::include_graphics(here::here("analysis/figures/flake-measurements-schematic-figure-temp.png"))
```

@@

# Results

@@

# References

@@

::: {#refs}
:::

@@

```{r}
#| label: colophon
#| cache: false

# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```
